Revisiting the Austral Spring Extratropical Southern Hemisphere zonally asymmetric circulation using complex Empirical Orthogonal Functions

### 2022-03-28 analysis/paper/shceof.Rmd
Render

```{r read-indices}
enso <- rsoi::download_oni(TRUE, data_path("raw", "oni.csv")) %>%
  as.data.table() %>%
  .[, .(time = lubridate::as_datetime(Date), oni = ONI)] %>%
  na.omit() %>%
  .[season(time) == "SON"] %>%
  .[, oni := oni*season_weights(time)] %>% 
  .[, .(oni = mean(oni)), by = .(time = seasonally(time))]

dmi <- rsoi::download_dmi(TRUE, data_path("raw", "dmi.csv")) %>%
  as.data.table() %>%
  .[, .(time = lubridate::as_datetime(Date), dmi = DMI)] %>%
  na.omit() %>%
  .[season(time) == "SON"] %>%
  .[, dmi := dmi*season_weights(time)] %>% 
  .[, .(dmi = mean(dmi)), by = .(time = seasonally(time))]

>>>>

```{r read-indices}
enso <- ENSO() %>%
  fread() %>% 
  .[, .(time = lubridate::as_datetime(Date), oni = ONI)] %>% 
  na.omit() %>%
  .[season(time) == "SON"] %>%
  .[, oni := oni*season_weights(time)] %>% 
  .[, .(oni = mean(oni)), by = .(time = seasonally(time))]

dmi <- DMI() %>%
  fread() %>% 
  .[, .(time = lubridate::as_datetime(Date), dmi = DMI)] %>% 
  na.omit() %>%
  .[season(time) == "SON"] %>%
  .[, dmi := dmi*season_weights(time)] %>% 
  .[, .(dmi = mean(dmi)), by = .(time = seasonally(time))]
